%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}

\begin{rSubsection}{Sony Interactive Entertainment, Japan}{\em Feburary 2024 - Present}{Senior Machine Learning Engineer}{}
\item Developing PlayStation Network.
\end{rSubsection}

\begin{rSubsection}{LY Corporation, Japan}{\em October 2023 - December 2024}{Multimodal research engineer}{}
\item Develop Lighthouse, an OSS library for reproducible video moment retrieval and highlight detection. URL: \url{https://github.com/line/lighthouse} (Our paper was accepted at EMNLP'24 Demo).
\item Develop hallucination detectors in large audio-video language models.
\item Enhance audio-visual representation learning using object detectors and CLAP.
\item Developed text-to-audio retrieval system. Our team participated in DCASE2024 competition.
\item Propose a novel text-audio task of ``language-based audio moment retrieval'' to retrieve relevant moments from long audio based on a text query.
\end{rSubsection}
\vspace{-0.5em}

\begin{rSubsection}{Apple, Japan}{\em January 2022 - May 2022}{Machine Learning Engineer Internship}{}
\item Developed machine learning models for unsupervised video anomaly detection.
\end{rSubsection}
\vspace{-0.5em}

\begin{rSubsection}{Preferred Networks, Japan}{\em August 2021 - March 2022}{Research Internship}{}
\item Worked on a multimodal FoodAI project as a part-time researcher and our paper was accepted at CEA++2022 and won the best paper award.
\end{rSubsection}
\vspace{-0.5em}

\end{rSection}